An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-24 VLDB2026/main.tex
1

	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited. To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios. Additionally, we further assess the robustness of each algorithm under varying conditions.

@@

\textcolor{orange}{On large-scale dataset Deep100M, besides the three methods already mentioned with long build times, we also find that graph-based algorithms using pruning strategies (such as FilteredDiskANN and UNG) exhibit significantly increased construction time, especially when the pruning is complex and extensive, leading to higher computational overhead. In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size, thanks to their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}

@@

>>>>

%	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited.
%	To fill this gap, we conduct a comprehensive experimental evaluation of hybrid query algorithms, analyzing the index construction costs and query efficiency across different scenarios. Additionally, we further assess the robustness of each algorithm under varying conditions.

	Moreover, beyond BigANN, systematic evaluations of hybrid query algorithms remain limited. \textcolor{orange}{Although existing work, such as the survey by \cite{compare}, reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms. To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios. Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications.}

@@

\textcolor{orange}{On large-scale dataset Deep100M, besides the three methods already mentioned with long build times, we also observe that algorithms based on Vamana (such as FilteredDiskANN and UNG) exhibit significantly increased construction time. Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead. 
In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size, thanks to their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}

@@

	\textcolor{orange}{For large-scale dataset, DSG only supports single-threaded construction, resulting in the longest build time.}
